### 2017-02-28 2017mergingmerges/section/XX-Proof.tex
mention Var1
S6 proof, S7 related some cuts

The @Soundness@ theorem above uses @EvalBs@ to evaluate the fused program, and @EvalOriginal@ ensures that the original program evaluates with that program's subset of the fused heap.
%%% AR: Really would like to say something about this but no room to explain properly
% For shared inputs when one program has pulled, the other program must be evaluated with the other value removed from the end of the stream.

>>>>

The @Soundness@ theorem above uses @EvalBs@ to evaluate the fused program, and @EvalOriginal@ ensures that the original program evaluates with that program's subset of the fused heap, using @Var1@ and @Var2@ to extract the variables.
Care must be taken to remove stream values that the other process has pulled but this one has not yet.
%%% AR: Really would like to say something about this but no room to explain properly
% For shared inputs when one program has pulled, the other program must be evaluated with the other value removed from the end of the stream.

### 2017-02-28 2017mergingmerges/section/XX-Related.tex
S6 proof, S7 related some cuts

This work aims to address the problems with current combinator-based array fusion systems.
As stated in the introduction, neither pull-based or push-based fusion is sufficient.
Some combinators are inherently push-based, particularly those with multiple outputs such as @unzip@; while others are inherently pull-based, such as @zip@.

Short cut fusion is an attractive idea, as it allows fusion systems to be specified with a single rewrite rule.
However, short cut fusion relies on inlining which, like pull-based streams, only occurs when there is a single consumer.
Thus, short cut fusion is inherently biased towards pull fusion.
Push-based short cut fusion systems \emph{do} exist \cite{gill1993short}, but support only the intersection of pull and push: that is, neither @zip@ nor @unzip@ \cite{svenningsson2002shortcut,lippmeier2013data}.

Recent work on stream fusion by \citet{kiselyov2016stream} uses staged computation in a push-based system to ensure all combinators are inlined, but when streams are used multiple times this causes excessive inlining, which duplicates work.
For effectful input streams, for example reading from the network, this duplicated work can change the overall meaning of the program.
% I could write more about this eg only supporting a single output, but the other points probably apply to push streams in general

Data flow fusion~\cite{lippmeier2013data} is neither pull-based nor push-based, and supports arbitrary splits and joins.
It supports standard combinators such as @map@, @filter@ and @fold@, and converts each stream to a series with explicit rate types, similar to the clock types of Lucid Synchrone \cite{benveniste2003synchronous}.
These rate types ensure that well-typed programs can be fused without introducing unbounded buffers.
This allows unfusable programs to be caught at compile time.
The main drawback of data flow fusion is that it only supports a limited set of combinators, and adding more is non-trivial.

One way to address the difference between pull and push streams is to explicitly support both separately, as seen in \citet{bernardy2015duality} and \citet{lippmeier2016polarized}.
Here, pull streams have the type @Source@ and are represented as a source that is always available to be pulled from, while push streams have the type @Sink@ and are represented as a sink that can always accept input.
Both systems rely on stream bindings being used linearly to ensure correctness, including boundedness of buffers and ordering of effects.
Operations over sources are expressed fairly naturally compared to streams, for example the @zip@ combinator has the type @Source a -> Source b -> Source (a,b)@.
Sinks, however, are co-variant, and operations must be performed somewhat backwards, so that the @unzip@ combinator takes the two output sinks to push into and returns a new sink that pushes into these.
It has the type @Sink a -> Sink b -> Sink (a,b)@.
This system requires the streaming computation to be manually split into sources and sinks, and be joined together by a loop that `drains' values from the source and pushes them into the sink.

>>>>

This work aims to address the limitations of current combinator-based array fusion systems.
As stated in the introduction, neither pull-based or push-based fusion is sufficient.
Some combinators are inherently push-based, particularly those with multiple outputs such as @unzip@; while others are inherently pull-based, such as @zip@.

Short cut fusion is an attractive idea, as it allows fusion systems to be specified by a single rewrite rule.
However, short cut fusion relies on inlining which, like pull-based streams, only occurs when there is a single consumer.
Thus, short cut fusion is inherently biased towards pull fusion.
Push-based short cut fusion systems \emph{do} exist \cite{gill1993short}, but support neither @zip@ nor @unzip@ \cite{svenningsson2002shortcut,lippmeier2013data}.

Recent work on stream fusion by \citet{kiselyov2016stream} uses staged computation in a push-based system to ensure all combinators are inlined, but when streams are used multiple times this causes excessive inlining, which duplicates work.
For effectful inputs such as reading from the network, duplicating work changes the semantics.
% I could write more about this eg only supporting a single output, but the other points probably apply to push streams in general

Data flow fusion~\cite{lippmeier2013data} is neither pull-based nor push-based, and supports arbitrary splits and joins.
It supports standard combinators such as @map@, @filter@ and @fold@, and converts each stream to a series with explicit rate types, similar to the clock types of Lucid Synchrone \cite{benveniste2003synchronous}.
These rate types ensure that well-typed programs can be fused without introducing unbounded buffers.
This allows unfusable programs to be caught at compile time.
However, it only supports a limited set of combinators, and adding more is non-trivial.

One way to address the difference between pull and push streams is to explicitly support both separately, as seen in \citet{bernardy2015duality} and \citet{lippmeier2016polarized}.
Here, pull streams have the type @Source@ and represent a source that is always available to be pulled from, while push streams have the type @Sink@ and represent a sink that can always accept input.
Both systems rely on stream bindings being used linearly to ensure correctness, including boundedness of buffers.
Operations over sources are expressed fairly naturally compared to streams, for example the @zip@ combinator has the type @Source a -> Source b -> Source (a,b)@.
Sinks, however, are co-variant, and operations must be performed somewhat backwards, so that the @unzip@ combinator takes the two output sinks to push into and returns a new sink that pushes into these.
It has the type @Sink a -> Sink b -> Sink (a,b)@.
This system requires the streaming computation to be manually split into sources and sinks, and be joined together by a loop that `drains' values from the source and pushes them into the sink.
